%%% Important. To have correct table numberings
\renewcommand{\thetable}{\thesection\alph{table}}

\chapter[Excellence]{Excellence}
\label{cha:excellence}
\instructions{
Your proposal must address a work programme topic for this call for proposals. \\
\textit{This section of your proposal will be assessed only to the extent that it is relevant to that topic.}\\
}

\section{Objectives}
\label{sec:objectives}
\instructions{
Describe the overall and specific objectives for the project1, which should be clear, measurable,
realistic and achievable within the duration of the project. Objectives should be consistent with
the expected exploitation and impact of the project (see section 2).
}

The European Space Agency's Gaia Mission \cite{2016A&A...595A...1G} is the most successful of ESA's space astronomy
missions as measured by the publication rate of papers using its data in one form or another \memo{(do we have a citation for that?)}. Over 2000 papers appeared
between April 2018 and December 2019 that use data from the second Gaia data release. Among the high profile science
results published by European groups are the discovery of a spiral in the phase space structure of the Milky Way's disk
(\cite{2018Natur.561..360A} indicative of a recent disturbance, most likely due to the Sagittarius dwarf galaxy), the
first direct observational evidence of crystallization in the interiors of white dwarfs \cite{2019Natur.565..202T} (confirming a fifty year old prediction), and the uncovering of a major event 10 billion years into the Milky Way's past
when a collision with a dwarf galaxy took place which contributed to the build-up of the Milky Way's stellar halo and
thick disk \cite{2018Natur.563...85H, 2018MNRAS.478..611B, 2019arXiv190904679B}. 

Many more exciting results have been reported and a common theme is that the astronomy community has so far mostly
focused (understandably) on the `low hanging fruit' in the Gaia data archive. This is manifest in the often drastic cuts
that are done on the quality of the Gaia data in order to obtain samples of stars for which the data analysis is
straightforward (avoiding for example the well known problems associated with the estimation of distance as the inverse
of the parallax \cite{2018A&A...616A...9L}), and in the ignoring of the properties of the Gaia survey itself, in
particular its completeness and source selection strategy. This means that many high-profile science cases that Gaia was
built for cannot be realized because the selection function of the Gaia survey combined with the data cuts leads to
unrepresentative samples from which, for example, the size scale of the structural components of the Milky Way cannot
reliably be derived.

The Gaia selection function is a highly non-trivial combination of the on-board selection of sources, telemetry
losses, selections on data quality during the data processing, and selection on quality before the publication of the
processed data in the Gaia archive \memo{(show examples in the scientific motivation section below)}. As a result, the
selection function for Gaia has only been characterized in highly simplified ways \memo{(provide literature references
in the motivation section below)} even though it will be crucial for a full exploitation of the intrinsic science
potential of the Gaia data, in particular also in view of the legacy value of the Gaia archive data which will remain
the standard in fundamental astrophysical data for decades to come.

The objective of this proposal is to build a detailed selection function for the Gaia data and to provide this to the
scientific community in the form of numerical tables and source code that allow users to apply the selection function to
their scientific analyses and thus maximize the outcome thereof. In detail the objectives are:

\begin{enumerate}
    \item Develop a detailed mathematical formulation of a survey selection function, where the goal is to keep this
        as general as possible even if in this project the focus is on the Gaia survey.  The formulation should account
        for the layering of user imposed sample selections on top of the survey selection function.
    \item Provide a detailed practical implementation of the Gaia selection function in the form of auxiliary data,
        which will be accessible through the ESA archive, and open source tools which will be made available through
        code hosting websites. 
    \item Develop tools to incorporate the selection function in scientific analyses. These tools should allow for
        combining the Gaia survey selection function with user imposed sample restrictions. The tools will be made
        available as open source code through code hosting websites.
    \item Apply the selection function tools to example science cases. This will serve to demonstrate the benefits of
        carefully accounting for the selection function and at the same time provide worked examples to the community of
        prospective users of these tools.
\end{enumerate}

\subsection{Context}
\label{sec:context}

ESA's Gaia mission \cite{2016A&A...595A...1G} represents a European breakthrough in astrophysics, a cornerstone
mission which was launched in 2013 aimed at producing the most accurate 3D map of the Milky Way to date. The resulting
stereoscopic census of our Galaxy represents a giant leap in astrometric accuracy (reaching the 10--20 micro-arcsecond
regime \memo{perhaps also give the relative improvement? e.g. we now know the distance to a well known star to this precision}) complemented by the only full sky homogeneous photometric survey with an angular resolution comparable to that
of the Hubble Space Telescope, as well as the largest spectroscopic survey ever undertaken. 

The primary scientific aim of the mission is to map the structure of our Galaxy and unravel its formation history and
subsequent evolution. Current cosmological models envisage the formation of large galaxies through the merging of
smaller structures. Deciphering the assembly history of our Galaxy requires a detailed mapping of the structure,
dynamics, chemical composition, and age distribution of its stellar populations. Ideally one would like to `tag'
individual stars to each of the progenitor building blocks of the Galaxy \cite{2002ARA&A..40..487F}. The Gaia mission is
designed to provide the required fundamental data in the form of distances (through parallaxes), space velocities
(through proper motions and radial velocities) and astrophysical characterisation (through multi-colour photometry) for
massive numbers of stars throughout most of the Galaxy. It should be stressed however that Gaia is not simply a `Milky
Way mission' but is truly a multi-faceted {\em astrophysics mission} which will provide exciting scientific results
covering many topics including: fundamental stellar physics across the Hertzsprung-Russell diagram, the characterisation of
tens of millions of binary stars, unique samples of variable stars of nearly all types (including key cosmological
distance calibrators), detection and orbital classification of thousands of extra-solar planetary systems, a
comprehensive survey of objects ranging from huge numbers of minor bodies in our Solar System, through galaxies in the
nearby Universe, to over a million distant quasars. Gaia will also provide a number of stringent tests of general
relativity. Last but not least, a massive survey such as Gaia will uncover many surprises that the Universe still holds
in store for us.

\begin{itemize}
    \item Mention data releases and successes so far.
    \item Briefly describe DPAC and explain why is it not doing the survey selection function.
\end{itemize}

\subsection{Scientific motivation}
\label{sec:scientific-motivation}

Detailed motivation of the need for a selection, use a few example science cases to make the point.

\begin{itemize}
    \item What prominent Gaia science cases cannot (ever?) be done without a well-defined and computationally tractable
        selection function
        \begin{itemize}
            \item Structural parameters of the Milky Way (disk scale length/height etc)
            \item Dark matter sub-halo finding through gaps in streams
            \item Binary population parameters (frequency, parameter distributions), but also stellar census (mass function of single stars)
            \item Exoplanet population parameters (frequency, parameter distributions)
            \item Local dark matter density
        \end{itemize}
    \item What is the selection function.
        \begin{itemize}
            \item Needs to be clearly defined and will probably require someone to work on the detailed definition and
                mathematical formulation (if the latter has not already been done).
            \item How does it relate to survey completeness; do we include completeness in the definition.
            \item Point out that multiple layers of selection may take place in any scientific investigation of Gaia or
                other astronomy data. The formulation/definition of the selection function should allow for layers of
                selection.
            \item To keep the work manageable in this project we will only provide the `basic' Gaia selection function.
                Accounting for the effect of additional user-imposed selection of data will be through tools also
                developed in this project.
        \end{itemize}
    \item Impact on the rest of astrophysics
        \begin{itemize}
            \item The Gaia catalogue is now being used to define target selection for other surveys (e.g. 4MOST). The completeness of these derivative surveys will be defined by the completeness of Gaia.
            \item We will implement selection functions for other surveys (e.g. APOGEE, LAMOST) in the open source software that we produce, that will enable users to, for example, calculate the odds of a star having a parallax in Gaia and a radial velocity in APOGEE.
        \end{itemize}
\end{itemize}

\section{Relation to the work programme}
\label{sec:relation-to-work-programme}
\instructions{
Indicate the work programme topic to which your proposal relates, and explain how your proposal
addresses the specific challenge and scope of that topic, as set out in the work programme.
}

This project related to the topic ``Scientific data exploitation'' (SPACE-30-SCI-2020 of the H2020 work programme). The
key points from the work programme addressed in this project are:
\begin{itemize}
    \item Enhances the scientific exploitation of data from a flagship European space mission. Relies on data from an ESA
        mission. The data from Gaia will have a legacy value for decades to come which is enormously enhanced by the
        availability of an accurately described selection function.
    \item Studies of the Gaia selection function must be done through comparison with other sky surveys (ground and
        space based). This combination of data will naturally also provide insight into the selection function of the
        other surveys.
    \item This work will lead to data products for the ESA Gaia archive.
    \item The work is done in international cooperation, specifically with partners from the space powers USA and
        Australia.
\end{itemize}

\section{Concept and methodology}
\label{sec:conceptandmethods}
\subsection{(a) Concept}
\label{sec:concept}
\instructions{
    \begin{itemize}
        \item Describe and explain the overall concept underpinning the project. Describe the main
            ideas, models or assumptions involved. Identify any inter-disciplinary considerations and,
            where relevant, use of stakeholder knowledge. Where relevant, include measures taken for
            public/societal engagement on issues related to the project. Describe the positioning of the
            project e.g. where it is situated in the spectrum from ‘idea to application’, or from ‘lab to
            market’. Refer to Technology Readiness Levels where relevant. (See General Annex G of the work
            program);
        \item Describe any national or international research and innovation activities which will be
            linked with the project, especially where the outputs from these will feed into the project;
    \end{itemize}
}

Develop and implement the Gaia selection through research to be conducted by four teams \memo{(co-I plus 1 or 2
postdocs, we'll see what can be financed)} and supported with the expertise form the US/Australian partners.

\subsection{(b) Methodology}
\label{sec:methods}
\instructions{
    \begin{itemize}
        \item Describe and explain the overall methodology, distinguishing, as appropriate, activities
            indicated in the relevant section of the work programme, e.g. for research, demonstration,
            piloting, first market replication, etc.
    \end{itemize}
}

\memo{The tasks below will be mapped to the work packages for this proposal. The WP descriptions will provide more
detail on the work to be done.}

\begin{enumerate}
    \item Operational definition selection/completeness function
        \begin{itemize}
            \item For arbitrary sky survey? More specific to Gaia?
            \item Mathematical formulation; account for multiple layers of selection (spacecraft, data processing, user)
            \item Handling unknown aspects of the selection function (for example information lost along with dropped
                spacecraft telemetry)
        \end{itemize}
    \item Practical realization of Gaia selection function
        \begin{itemize}
            \item Gather the necessary information (on-board detection/selection, filtering during data processing,
                statistics on Gaia sources, …)
            \item Collect data from other surveys
            \item Study spatial resolution limitations
            \item Translate basic selection steps to effect on source astrophysical parameter distributions (stellar
                parameters, binary parameters, population stats, …)
            \item Define a “baseline” selection function as starting point for adding the effect of user defined
                selection steps
        \end{itemize}
    \item Develop tools (code+data) to incorporate selection function in scientific analyses
        \begin{itemize}
            \item Layer user choices onto baseline selection function(s)
            \item How to make this available
            \item Documentation
        \end{itemize}
    \item Apply the selection function tools to selected science cases.
\end{enumerate}

\section{Ambition}
\label{sec:ambition}
\instructions{
    \begin{itemize}
        \item Describe the advance your proposal would provide beyond the state-of-the-art, and the
            extent the proposed work is ambitious.
        \item Describe the innovation potential (e.g. ground-breaking objectives, novel concepts and
            approaches, new products, services or business and organisational models) which the proposal
            represents. Where relevant, refer to products and services already available on the market.
            Please refer to the results of any patent search carried out.
    \end{itemize}
}

\begin{itemize}
    \item Currently no selection function is available for Gaia catalogue, only ad-hoc implementations for specific
        science cases.
        \begin{itemize}
            \item Most works in the end ignore selection function effects.
        \end{itemize}
    \item Readily available selection function will enhance all scientific analyses of Gaia data and lead to much better
        reproducibility of results.
    \item This project will result in clearer definition of selection function concept, which can be applied to other
        surveys too.
    \item Expertise gained in this project can be transferred to other surveys.
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proposal-main"
%%% End:
