\subsubsection{Universiteit Leiden}
\label{sec:ulei}

\paragraph{General description}
Leiden Observatory is the astronomy department at Leiden University, 
where world-class research is conducted covering areas of observational 
and theoretical astrophysics, instrumentation, and laboratory astrophysics. 
Leiden Observatory provides an environment where astronomers can
be consulted directly on their wishes for the Gaia selection function and
its practical implementation.

\paragraph{Key persons}
Dr.~Anthony Brown (male) is a faculty member of Leiden Observatory. He has published over 75 papers in the peer-reviewed literature, and supervised 9 PhD students and several postdocs. He has been deeply involved with the Gaia mission since 1997, having contributed to the optimization of the mission, the preparations for the data processing, and the implementation of several algorithms in the DPAC data processing pipelines. He currently serves as the chair of the Gaia Data Processing and Analysis Consortium and is a member of the Gaia Science Team. The efforts described in this proposal will very much benefit from the extensive expertise of Brown on both the Gaia spacecraft and its instruments as well as the DPAC processing pipelines. The close connections to ESA and DPAC through Brown's role in the latter will facilitate the communications regarding details of the selection function, the integration of the results in the Gaia archive, and the transfer of expertise to DPAC.

\paragraph{Relevant publications}
\begin{itemize}
    \item Gaia Collaboration, Brown, et al., 2018, Gaia Data Release 2. Summary of the contents and survey properties, A\&A 616, A1 
    \item Snellen \& Brown, 2018, The mass of the young planet Beta Pictoris b through the astrometric motion of its host star, Nature Astronomy 2, 883 
    \item Zari, Hashemi, Brown, et al., 2018, 3D mapping of young stars in the solar neighbourhood with Gaia DR2, A\&A 620, A172 
    \item  Luri, Brown, et al., 2018, Gaia Data Release 2. Using Gaia parallaxes, A\&A 616, A9 
    \item Helmi, Babusiaux, Koppelman, Massari, Veljanoski, Brown, 2018, The merger that led to the formation of the Milky Way's inner stellar halo and thick disk, Nature 563, 7729 
\end{itemize}

\paragraph{Relevant previous projects}
Brown was the main contact point at ULEI for the following projects:
\begin{itemize}
    \item FP6 ELSA Marie-Curie Research Training Network
    \item ESF GREAT Research Network Programme 
    \item FP7 GREAT Marie-Curie Initial Training Network
    \item FP7 GENIUS Collaborative project (SPA.2013.2.1-01 Exploitation of space science and exploration data)
    \item BIG-SKY-EARTH Trans Domain COST Action
\end{itemize}

\paragraph{Significant infrastructure}
At Leiden Observatory Undergraduate courses are given at all levels. The 
graduate programme currently involves 80 PhD students. Leiden 
Observatory shares a building with the Lorentz centre, an international 
centre for workshops in the sciences which offers excellent facilities for 
hosting workshops, conferences, and schools. In particular, office space is 
available for bringing researchers together for extended periods. 
Brown has a leading role in the Gaia project, being the chair of the 
Executive of the Data Processing and Analysis Consortium. 